### 2020-11-09 README.Rmd
Revert "Trying to make this no longer behave like an R package.  Might break things."
This reverts commit 32734dcbc63e2e1005f6aac130f5329c997f1c55.

<!-- badges: start -->
[![Binder](https://mybinder.org/badge_logo.svg)](https://mybinder.org/v2/gh/BrunaLab/HeliconiaDemography/master?urlpath=rstudio)
[![R build status](https://github.com/BrunaLab/HeliconiaDemography/workflows/run-tests/badge.svg)](https://github.com/BrunaLab/HeliconiaDemography/actions)
<!-- badges: end -->

>>>>

<!-- badges: start -->
[![Binder](https://mybinder.org/badge_logo.svg)](https://mybinder.org/v2/gh/BrunaLab/HeliconiaDemography/master?urlpath=rstudio)
[![R build status](https://github.com/BrunaLab/HeliconiaDemography/workflows/R-CMD-check/badge.svg)](https://github.com/BrunaLab/HeliconiaDemography/actions)
<!-- badges: end -->
